Preregistration analysis, Cost 2 study

### 2019-08-05 Cost2/Cost2_prereg.Rmd
data column names are better matched now (Cost and Offer), and the scripts work well with them

# plot logistic (for the prop complete test, mainly, but it can be easily expanded for more flexibility in n-params)
plotLogis <- function(coeffs = 1, group = "Cognitive", handling = 1:14, reward = 1:20, xAxis = "Reward", plotType = lines, color = "black", lType = 1, pchType = 16){

@@

    # now the parameters
    label = "Reward Amount"
    if (group == "Cognitive"){cog = 1} else {cog = 0}
    if (group == "Phys"){phys = 1} else {phys = 0}
    if (group == "Easy") {easy = 1} else {easy = 0}
    if (xAxis == "Reward"){
        xAxis = reward 
        label = "Reward Amount" 
    } else {
        xAxis = handling
        label = "Handling Time"
    }

@@

        # earnings
        tempSummary[subj,3] <- sum(Data[[subj]]$Reward[tempChoice==1])

@@

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  mutate(rawChoice = Choice,
         RT = ifelse(RT > 14.1, 14, RT),
         Choice = ifelse(Choice == 2, 1, Choice),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         optimal = case_when(
          (Handling == 10 & Reward < 8) ~ 0,
          (Handling == 14 & Reward < 20) ~ 0,
          TRUE ~ 1
         ))

@@

``` {r 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
# filterout errors and compute R + H logistic per subject, then get coefficients
logisRH <- dataAll %>%
  filter(Choice < 2) %>%
  plyr::dlply("SubjID", identity) %>%
  lapply(function(data) {glm(Choice ~ Handling + Reward, data = data, family = "binomial")}) %>%
  sapply(coefficients)

# Rank sum tests
rankHand <- wilcox.test(logisRH["Handling", ])
rankReward <- wilcox.test(logisRH["Reward", ])

# Plot coeffs
temp <- melt(logisRH[c("Handling", "Reward"), ])
qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
  labs(x = "", y = "Coefficients") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = c(0.9, 0.7),
       panel.grid.major = element_blank(), 
       panel.grid.minor = element_blank(), 
       panel.background = element_blank(), 
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))
```

The plot shows the pooled coefficients across subjects for the effect of each predictor. The results show the expected discounting effect of increasing the handling time, as well as the increase in acceptance likelihood as a function of reward increments. We found that these coefficients were significantly different from zero for both handling (V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) and reward (V = `r rankReward$statistic`, p `r ifelse(rankReward$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) regardless of cost condition.

@@

``` {r 16.1.2., echo = FALSE, include = FALSE}
# add an AR regressor to track recent quits
logisRHAR <- dataAll %>%
              filter(Choice < 2) %>%
              group_by(SubjID) %>%
              mutate(AR = seqQuits(Choice)) %>%
              plyr::dlply("SubjID", identity) %>%
              lapply(function(data) {glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial")})

@@

``` {r 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
# calculate the proportions and earnings per subject, while keeping group info
temp <- dataAll %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID, Cost) %>%
  summarise(Earnings = sum(Reward[Choice == 1] / 100),
            pComplete = mean(Choice)) %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

@@

``` {r 16.1.4., echo=FALSE}
# in order
# clean data, 
# calculate each individual's prop. accept,
# calculate t.tests with optimality as null mean,
# correct pvalues with FDR
temp <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Handling, Reward, Cost) %>%
  summarise(pAccept = mean(Choice)) %>%
  mutate(optimal = case_when(
          (Handling == 10 & Reward < 8) ~ 0,
          (Handling == 14 & Reward < 20) ~ 0,
          TRUE ~ 1
        )) %>% 
  group_by(Handling, Reward, Cost) %>%
  summarise(meanAccept = mean(pAccept),
            sdAccept = sd(pAccept),
            optimal = unique(optimal),
            pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
  mutate(FDR = p.adjust(pvals, method = "BY"),
         significant = FDR < 0.05)

@@

``` {r 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
## ECDF of proportion completed per cost type
temp <- dataAll %>%
        filter(Choice < 2) %>%
        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Reward[rawChoice == 1] / 100),
                  pAccept = mean(Choice))

@@

*In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors. Reward and handling time will be within-subject factors, and condition a between-subjects factor. In support of hypotheses 4.1. and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions.*

``` {r 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
temp <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Reward) %>%
        summarise(pAccept = mean(Choice))

## REPEATED MEASURES ANOVA
# I think I like this the most
prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Reward + 
                                 Error(SubjID / (Handling * Reward))))

@@

``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
# prep data to plot the p(accept) based on reward, handling time and cost type
trueProp <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Reward, optimal) %>%
        summarise(pAccept = mean(Choice)) %>%
        group_by(Cost, Handling, Reward, optimal) %>%
        summarise(meanComplete = mean(pAccept),
                  SE = sd(pAccept) / sqrt(length(pAccept)))

# and plot
(a1 <- ggplot(data = trueProp, aes(interaction(Reward, Handling), meanComplete, color = Cost)) + 
        geom_point(size = 3) + 
        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Reward.Handling", y = "Proportion Accepted") +
        scale_color_manual(values = cols) +
        theme(legend.key = element_blank(),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 16)))

@@

``` {r 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
mixLogis_main <- list()
mixData <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Cost, Handling, Reward) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice)) %>%
  ungroup()

# model with a random intercept and cost-type slope, then relevel the cost to get all pairwise comparisons
# the correct way to model a logistic with proportions as dependent vars is by prividing n of hits and quits as a matrix
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)

@@

``` {r 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Quasibinomial GLM versions (with proper proportion setup)
mixLogis_compare <- list()
mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$Handling <- glmer(cbind(totalAccepted, totalQuits) ~ Handling + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Reward + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$AllMain <- mixLogis_main$Wait
mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Reward + (Cost | SubjID), family = "binomial", data = mixData)

@@

``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# # pre
# t1 <- dataAll %>%
#   filter(Choice < 2, Half == "Half_1") %>%
#   group_by(SubjID) %>%
#   filter(Handling == 10) %>%
#   group_by(SubjID, Cost, Reward) %>%
#   summarise(pAccept = mean(Choice)) %>%
#   group_by(Cost, Reward) %>%
#   summarise(propAccept = mean(pAccept),
#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
#   ungroup() %>%
#   mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
#   ggplot(aes(Reward, propAccept, color = Cost)) +
#     geom_point(size = 3, show.legend = F) +
#     geom_line(show.legend = F) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
#     scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
#     labs(y = "Proportion Accepted", title = "First Half") +
#     theme(legend.key = element_blank(),
#           legend.position = c(0.8, 0.25),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
# 
# # post half
# t2 <- dataAll %>%
#   filter(Choice < 2, Half == "Half_2") %>%
#   group_by(SubjID) %>%
#   filter(Handling == 10) %>%
#   group_by(SubjID, Cost, Reward) %>%
#   summarise(pAccept = mean(Choice)) %>%
#   group_by(Cost, Reward) %>%
#   summarise(propAccept = mean(pAccept),
#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
#   ungroup() %>%
#   mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
#   ggplot(aes(Reward, propAccept, color = Cost)) +
#     geom_point(size = 3, show.legend = F) +
#     geom_line(show.legend = F) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
#     scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
#     labs(y = "", title = "Second Half") +
#     theme(legend.position = c(0.8, 0.2),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
# 
# 
# 
# grid.arrange(t1, t2, ncol = 2)

dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID) %>%
  filter(Handling == 10) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Block", "Last Block")) %>%
  group_by(SubjID, Half, Cost, Reward) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Half, Cost, Reward) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs)) %>%
  ungroup() %>%
  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
  ggplot(aes(Reward, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = F) +
    geom_line(size = 1, show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted") +
    facet_wrap(vars(Half), ncol = 2) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

@@

``` {r 16.3.2. mix pre/post separately, echo = FALSE, fig.align="center", fig.width = 5, fig.height = 4}
## compute the same mixed effects logistic for each half
# mixed logistic for the first half
mixLogis_pre <- list()
mixData <- dataAll %>%
  filter(Half == "Half_1") %>%
  group_by(SubjID, Cost, Handling, Reward) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)

# mixed logistic for the second half
mixLogis_post <- list()
mixData <- dataAll %>%
  filter(Half == "Half_2") %>%
  group_by(SubjID, Cost, Handling, Reward) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

>>>>

# plot logistic (for the prop complete test, mainly, but it can be easily expanded for more flexibility in n-params)
plotLogis <- function(coeffs = 1, group = "Cognitive", handling = 1:14, reward = 1:20, xAxis = "Offer", plotType = lines, color = "black", lType = 1, pchType = 16){

@@

    # now the parameters
    label = "Offer Amount"
    if (group == "Cognitive"){cog = 1} else {cog = 0}
    if (group == "Phys"){phys = 1} else {phys = 0}
    if (group == "Easy") {easy = 1} else {easy = 0}
    if (xAxis == "Offer"){
        xAxis = reward 
        label = "Offer Amount" 
    } else {
        xAxis = handling
        label = "Handling Time"
    }

@@

        # earnings
        tempSummary[subj,3] <- sum(Data[[subj]]$Offer[tempChoice==1])

@@

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  mutate(rawChoice = Choice,
         RT = ifelse(RT > 14.1, 14, RT),
         Choice = ifelse(Choice == 2, 1, Choice),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         optimal = case_when(
          (Handling == 10 & Offer < 8) ~ 0,
          (Handling == 14 & Offer < 20) ~ 0,
          TRUE ~ 1
         ))

@@

``` {r 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
# filterout errors and compute R + H logistic per subject, then get coefficients
logisRH <- dataAll %>%
  filter(Choice < 2) %>%
  plyr::dlply("SubjID", identity) %>%
  lapply(function(data) {glm(Choice ~ Handling + Offer, data = data, family = "binomial")}) %>%
  sapply(coefficients)

# Rank sum tests
rankHand <- wilcox.test(logisRH["Handling", ])
rankOffer <- wilcox.test(logisRH["Offer", ])

# Plot coeffs
temp <- melt(logisRH[c("Handling", "Offer"), ])
qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
  labs(x = "", y = "Coefficients") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = c(0.9, 0.7),
       panel.grid.major = element_blank(), 
       panel.grid.minor = element_blank(), 
       panel.background = element_blank(), 
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))
```

The plot shows the pooled coefficients across subjects for the effect of each predictor. The results show the expected discounting effect of increasing the handling time, as well as the increase in acceptance likelihood as a function of reward increments. We found that these coefficients were significantly different from zero for both handling (V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) and reward (V = `r rankOffer$statistic`, p `r ifelse(rankOffer$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) regardless of cost condition.

@@

``` {r 16.1.2., echo = FALSE, include = FALSE}
# add an AR regressor to track recent quits
logisRHAR <- dataAll %>%
              filter(Choice < 2) %>%
              group_by(SubjID) %>%
              mutate(AR = seqQuits(Choice)) %>%
              plyr::dlply("SubjID", identity) %>%
              lapply(function(data) {glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial")})

@@

``` {r 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
# calculate the proportions and earnings per subject, while keeping group info
temp <- dataAll %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID, Cost) %>%
  summarise(Earnings = sum(Offer[Choice == 1] / 100),
            pComplete = mean(Choice)) %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

@@

``` {r 16.1.4., echo=FALSE}
# in order
# clean data, 
# calculate each individual's prop. accept,
# calculate t.tests with optimality as null mean,
# correct pvalues with FDR
temp <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Handling, Offer, Cost) %>%
  summarise(pAccept = mean(Choice)) %>%
  mutate(optimal = case_when(
          (Handling == 10 & Offer < 8) ~ 0,
          (Handling == 14 & Offer < 20) ~ 0,
          TRUE ~ 1
        )) %>% 
  group_by(Handling, Offer, Cost) %>%
  summarise(meanAccept = mean(pAccept),
            sdAccept = sd(pAccept),
            optimal = unique(optimal),
            pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
  mutate(FDR = p.adjust(pvals, method = "BY"),
         significant = FDR < 0.05)

@@

``` {r 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
## ECDF of proportion completed per cost type
temp <- dataAll %>%
        filter(Choice < 2) %>%
        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Offer[rawChoice == 1] / 100),
                  pAccept = mean(Choice))

@@

*In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors. Offer and handling time will be within-subject factors, and condition a between-subjects factor. In support of hypotheses 4.1. and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions.*

``` {r 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
temp <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Offer) %>%
        summarise(pAccept = mean(Choice))

## REPEATED MEASURES ANOVA
# I think I like this the most
prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Offer + 
                                 Error(SubjID / (Handling * Offer))))

@@

``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
# prep data to plot the p(accept) based on reward, handling time and cost type
trueProp <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Offer, optimal) %>%
        summarise(pAccept = mean(Choice)) %>%
        group_by(Cost, Handling, Offer, optimal) %>%
        summarise(meanComplete = mean(pAccept),
                  SE = sd(pAccept) / sqrt(length(pAccept)))

# and plot
(a1 <- ggplot(data = trueProp, aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
        geom_point(size = 3) + 
        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Offer.Handling", y = "Proportion Accepted") +
        scale_color_manual(values = cols) +
        theme(legend.key = element_blank(),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 16)))

@@

``` {r 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
mixLogis_main <- list()
mixData <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice)) %>%
  ungroup()

# model with a random intercept and cost-type slope, then relevel the cost to get all pairwise comparisons
# the correct way to model a logistic with proportions as dependent vars is by prividing n of hits and quits as a matrix
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)

@@

``` {r 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Quasibinomial GLM versions (with proper proportion setup)
mixLogis_compare <- list()
mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$Handling <- glmer(cbind(totalAccepted, totalQuits) ~ Handling + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$Offer <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$AllMain <- mixLogis_main$Wait
mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (Cost | SubjID), family = "binomial", data = mixData)

@@

``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# # pre
# t1 <- dataAll %>%
#   filter(Choice < 2, Half == "Half_1") %>%
#   group_by(SubjID) %>%
#   filter(Handling == 10) %>%
#   group_by(SubjID, Cost, Offer) %>%
#   summarise(pAccept = mean(Choice)) %>%
#   group_by(Cost, Offer) %>%
#   summarise(propAccept = mean(pAccept),
#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
#   ungroup() %>%
#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
#   ggplot(aes(Offer, propAccept, color = Cost)) +
#     geom_point(size = 3, show.legend = F) +
#     geom_line(show.legend = F) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
#     scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
#     labs(y = "Proportion Accepted", title = "First Half") +
#     theme(legend.key = element_blank(),
#           legend.position = c(0.8, 0.25),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
# 
# # post half
# t2 <- dataAll %>%
#   filter(Choice < 2, Half == "Half_2") %>%
#   group_by(SubjID) %>%
#   filter(Handling == 10) %>%
#   group_by(SubjID, Cost, Offer) %>%
#   summarise(pAccept = mean(Choice)) %>%
#   group_by(Cost, Offer) %>%
#   summarise(propAccept = mean(pAccept),
#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
#   ungroup() %>%
#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
#   ggplot(aes(Offer, propAccept, color = Cost)) +
#     geom_point(size = 3, show.legend = F) +
#     geom_line(show.legend = F) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
#     scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
#     labs(y = "", title = "Second Half") +
#     theme(legend.position = c(0.8, 0.2),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
# 
# 
# 
# grid.arrange(t1, t2, ncol = 2)

dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID) %>%
  filter(Handling == 10) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Block", "Last Block")) %>%
  group_by(SubjID, Half, Cost, Offer) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Half, Cost, Offer) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs)) %>%
  ungroup() %>%
  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  ggplot(aes(Offer, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = F) +
    geom_line(size = 1, show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted") +
    facet_wrap(vars(Half), ncol = 2) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

@@

``` {r 16.3.2. mix pre/post separately, echo = FALSE, fig.align="center", fig.width = 5, fig.height = 4}
## compute the same mixed effects logistic for each half
# mixed logistic for the first half
mixLogis_pre <- list()
mixData <- dataAll %>%
  filter(Half == "Half_1") %>%
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)

# mixed logistic for the second half
mixLogis_post <- list()
mixData <- dataAll %>%
  filter(Half == "Half_2") %>%
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
mixLogis_post$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
mixLogis_post$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
